Price of Anarchy for Mean Field Games

### 2018-07-22 PoA.tex
update proposition 5

%proposition b_2 \to 0
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
\label{prop:b2_to_0}
\end{proposition}

\begin{proof}
	If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.

	As $b_2 \to 0$, we have $\lambda \to 0 $ and
	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$u_t \xrightarrow[b_2 \to 0 ]{} 0.$$

	From equation (\ref{eq:x_bar_MFG_explicit}), we have $\bar{x}_t^{MFG}=\mathbb{E}(\xi) e^{\int_0^t(b_1+\bar{b}_1-Bu_s)ds}$, and therefore, $\bar{x}_t^{MFG} \to \mathbb{E}(\xi) \exp((b_1+\bar{b}_1)t) =: \bar{x}_t^{MFG,0,b_2}$, which is bounded over $[0,T]$. Moreover, since $B^{0,b_2}>0, B^{0,b_2}C^w >0, B^{0,b_2}D^w \geq 0$, we still have the unique solution for $w^{0,b_2}_t$ when $b_2 \to 0$.

	Hence, from Proposition \ref{prop:diff_SC}, the bounded convergence theorem, and the assumption on $\xi$, we deduce
	\begin{equation*}
	\begin{split}
	\lim_{b_2 \to 0} \Delta SC &= \frac{1}{2} B^{0,b_2} \int_0^T (w_t^{0,b_2} \cdot \bar{x}_t^{MFG,0,b_2})^2 dt,\\
	0<&\lim_{b_2 \to 0} \Delta SC < \infty,
	\end{split}
	\end{equation*}

	Since $B^{\eta} \to 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, we get:
	\begin{equation*}
	\begin{split}
	\text{when } A^\eta \neq 0, \qquad & \eta_t \to \eta^{0,b_2}_t := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} },\\
	\text{when } A^{\eta} = 0, \qquad & \eta_t \to \eta^{0,b_2}_t := D^{\eta} - C^{\eta}(T-t),
	\end{split}
	\end{equation*}
	which are bounded over $[0,T]$. Thus, the variance function $ v_t $ converges to some positive bounded function $ v^{0,b_2}_t := Var(\xi)e^{2b_1t}+ \sigma^2 \int_0^t e^{2b_1(t-s)}ds>0$ for every given time $t\in [0,T]$.
	Using the fact that $w^{0,b_2}_t\not \equiv 0$  and together with equation (\ref{eq:SC_MKV_2}), we have $0< \lim_{b_2\to 0} SC^{MKV} <\infty $ .

	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we obtain $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{0,b_2} > 1.$$

>>>>

%proposition b_2 \to 0
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and assuming $b_1 > 0$.

	If $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
\label{prop:b2_to_0}
\end{proposition}

\begin{proof}
	If $\bar{b}_2 =0$, we have 
	\begin{equation*}
		B^{b_2} \xrightarrow[b_2 \to 0]{} 0, \quad B^{\eta,b_2} \xrightarrow[b_2 \to 0]{} 0, \quad \lambda = \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}
	\end{equation*}
	and $(A^{u},C^{u}, D^{u}), (A^{w}, C^{w}, D^{w}), (A^\eta, C^\eta, D^\eta)$ are all independent of $b_2$. We can then use the same technique shown in Proposition \ref{prop:r_bar_r} to conclude that 
	$$\lim_{b_2 \to 0} PoA = 1.$$

	Now, let's assume $\bar{b}_2 > 0$.	As $b_2 \to 0$, we have 
	\begin{equation*}
	\begin{array}{l}
		\lambda \longrightarrow 0\\
		\displaystyle B^{b_2} \longrightarrow{}  \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{b_2 \to 0} >0, \qquad B^{\eta,b_2} \longrightarrow{} 0 \\
		C^{u,b_2} \longrightarrow{} 0, \  D^{u,b_2} \longrightarrow{} 0 
	\end{array}
	\end{equation*}
	and $A^u, (A^w, C^w, D^w), (A^\eta, C^\eta, D^\eta)$ are independent of $b_2$.
	Moreover, we have $\delta^{+,b_2}_u \xrightarrow{} -2A^u >0 $ and $\delta^{-,b_2}_u \to 0$, so that $\delta^{+}_u - \delta^{-}_u \xrightarrow{} -2 A^u > 0$. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$u^{b_2}_t \xrightarrow[b_2 \to 0 ]{} 0 .$$
	Similar to the case in Proposition \ref{prop:r_bar_r}, we can derive an uniform bound for $u_t^{b_2}$ over $[0,T]$ for any $b_2$ small enough. Indeed, for any fixed $\epsilon >0$ there exits $b_2^* >0$ such that for any $b_2 \leq b_2^*$, $\max \{B^{b_2}, C^{u,b_2}, D^{u,b_2} \} \leq B^{b_2 \to \infty} + \epsilon =: c_1$ and
	\begin{equation*}
	 \vert u_t^{b_2} \vert \leq \frac{c_1 + 2 \epsilon \sqrt{(A^u)^2 + c_1^2} }{- 2 A^u e^{-2T \sqrt{(A^u)^2 + c_1^2} } } =: c_2 ,\qquad \forall  \  t \in [0,T]
	\end{equation*}

	From equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we have $\displaystyle \bar{x}_t^{MFG,b_2}=\mathbb{E}(\xi) \exp \left( \int_0^t(b_1+\bar{b}_1-B^{b_2} u^{b_2}_s)ds\right)$, and by the bounded convergence theorem we derive that for any fixed $t \in [0,T]$:
	$$\bar{x}_t^{MFG,b_2} \xrightarrow[b_2 \to \infty]{} \mathbb{E}(\xi) e^{(b_1+\bar{b}_1)t} =: \bar{x}_t^{MFG,b_2 \to 0} > 0$$

	Moreover, since $B^{b_2 \to 0}>0, B^{b_2 \to 0}C^w >0, B^{b_2\to 0}D^w \geq 0$, the limiting solution for $w_t^{b_2}$ is still well defined, denoted by $w_t^{b_2 \to 0}$, which is strictly positive over $[0,T]$. We also have $w_t^{b_2}$ is uniformly bounded over $[0,T]$ for all $b_2$ small enough.

	Hence, from Proposition \ref{prop:diff_SC}, the Bounded Convergence theorem, and the assumption on $\xi$, we deduce
	\begin{equation*}
	\lim_{b_2 \to 0} \Delta SC = \frac{1}{2} B^{b_2\to 0} \int_0^T (w_t^{b_2 \to 0} \cdot \bar{x}_t^{MFG,b_2 \to 0})^2 dt >0.
	\end{equation*}

	Since $B^{\eta,b_2} \to 0, A^{\eta} < 0, C^{\eta} >0$, and $D^{\eta} \geq 0$, using the same argument shown in Proposition \ref{prop:r_bar_r}, 
	we deduce that $\eta_t^{b_2}$ is uniformly bounded over $[0,T]$ for any $b_2$ small enough and $\eta_t^{b_2}$ converge pointwisely to a strictly positive function $\eta_t^{b_2 \to 0}$. More precisely, we can have
	$$\eta_t^{b_2 \to 0} := \left(D^{\eta} - \frac{C^{\eta}}{2A^\eta}\right) e^{-2A^\eta(T-t)} + \frac{C^\eta}{2A^{\eta} }.$$
	Again, with equation (\ref{eq:v_t_new_notation}) and the Bounded Convergence theorem, the variance function $v_t^{b_2}$ converges pointwisely to some strictly positive continuous function $\displaystyle v_t^{b_2 \to 0} := Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds$. We can then obtain that
	$$ 0 < \lim_{b_2 \to 0} SC^{MKV} < \infty.$$

	Therefore, combined with equation (\ref{eq:PoA_LQ_new_notation}), we conclude that $$\lim_{b_2 \to 0} PoA = 1 + \frac{\displaystyle \lim_{b_2 \to 0}\Delta SC}{\displaystyle \lim_{b_2 \to 0} SC^{MKV} } =: PoA^{b_2 \to 0} > 1.$$
